Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 introduction.tex
In introduction, clarified that AIC and compact binary coalescence are two possible channels, but not mutually exclusive
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1223 ccdd05d5-56c1-461a-bf98-85f6876523b4
Tuned paragraph in introduction describing S6/VSR3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1224 ccdd05d5-56c1-461a-bf98-85f6876523b4

Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with ejecta \citep{Bucciantini2011}.  A
proto-magnetar may form from accretion-induced collapse or the merger of two
\textsc{ns}s.  An accompanying \GW{} observation would confirm the latter.

In October 2010, \LIGO{}\footnote{\url{http://www.ligo.org/}} completed its
sixth science run (S6) and Virgo\footnote{\url{http://www.ego-gw.it/}}
completed its third science run (VSR3).  While both \LIGO{} detectors and Virgo
were operating, several all-sky detection pipelines operated in a low-latency
configuration to send astronomical alerts, namely \textsc{mbta}, Coherent
WaveBurst, and Omega \citep{HugheyGWPAW2011, S6lowlatency2, S6lowlatency3, S6lowlatency4}. The S6 analyses
achieved latencies of 30--60 minutes, which were dominated by a human vetting
process. Candidates were sent for \EM{} followup to several telescopes; Swift,
\textsc{rotse}, \textsc{tarot}, and Zadko \citep{kanner2008, HugheyGWPAW2011}
imaged some of the most likely sky locations.  \textsc{mbta} achieved the best
\GW{} trigger-generation latencies of 2--5 minutes.

>>>>

Interestingly, roughly a quarter to half of observed short
\GRB{}s also exhibit extended emission of $30$--$100$\,s in duration beginning
$\sim$$10$\,s after the \GRB{} and carrying comparable fluence to the initial
outburst.  Potential explanations for the emission are delayed fall-back
accretion caused by $r$-process heating \citep{Metzger2010} or the formation of
a proto-magnetar that interacts with ejecta \citep{Bucciantini2011}.  A
proto-magnetar may form from accretion-induced collapse or the merger of two
\textsc{ns}s.  An accompanying \GW{} observation would confirm the existence of
the latter channel.

In October 2010, \LIGO{}\footnote{\url{http://www.ligo.org/}} completed its
sixth science run (S6) and Virgo\footnote{\url{http://www.ego-gw.it/}}
completed its third science run (VSR3).  While both \LIGO{} detectors and Virgo
were operating, several all-sky detection pipelines operated in a low-latency
configuration to send astronomical alerts, namely \textsc{mbta}, Coherent
WaveBurst, and Omega \citep{HugheyGWPAW2011, S6lowlatency2, S6lowlatency3, S6lowlatency4}.
\textsc{mbta} achieved the best \GW{} trigger-generation latencies of 2--5 minutes.
Alerts were sent with latencies of 30--60 minutes, dominated by human vetting.
Candidates were sent for \EM{} followup to several telescopes; Swift,
\textsc{rotse}, \textsc{tarot}, and Zadko \citep{kanner2008, HugheyGWPAW2011}
imaged some of the most likely sky locations.
